Invasive chameleons released from predation display more conspicuous colors

### 2021-12-02 ms.Rmd
added proper sleect

>>>>

# Table S6
tableS6 <- as.data.frame(rbind(robust_localAdapt_DispBgrdAC_s6,
                               robust_DispBgrdCC_s6,
                               robust_CourtshipAC_s6,
                              robust_CourtshipCC_s6))
tableS6$Parameter <- rownames(tableS6)
rownames(tableS6) <- NULL

# Clean
final_S6 <- tableS6 %>% 
  mutate(SocialContext = c("Male-Male Display", rep("", 9), "Courtship Display", rep("", 9)),
         VisualRealm = c("Luminance  Contrast", rep("", 4), "Chromatic Contrast", rep("", 4), 
                         "Luminance Contrast", rep("", 4), "Chromatic Contrast", rep("", 4))) %>%
  dplyr::select(SocialContext, VisualRealm, Parameter, beta, SE, df, CI_L, CI_U)
write.csv(tableS6, file = "./output/tables/tableS6.csv", row.names = FALSE)
